---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?




#Inferential Results

Looking only at the graphical and numerical results alone is not enough to tell us if these results can explain if the aids drug is sex specific or not. To do this, we will need to run an inferential test. The one we will use is the chi-square test. 

We will now need to run nine **chisqtestGC** function from the tigerstats package. We will run each test with the assumption that the aids drug is sex specific.



# South Carolina

###As a Whole

$H_0$ The aids drug is not effective. (Independent)

$H_a$ The aids drug is effective.


```{r}
Scarolina_table <- xtabs(~infected + group, data = Scarolina)
chisqtestGC(Scarolina_table)
```


The p-value is 89%, we accept the null hypothesis. We can assume that the drug is not effective.

We will subset the data by sex to see if the drug is sex specific.

###FEMALES



$H_0$ The aids drug is not specific to females. (Independent)

$H_a$ The aids drug is specific to females. 

```{r}
ScarolinaF <- filter(Scarolina, sex=="F")
ScarolinaF_table <- xtabs(~infected + group, data = ScarolinaF)
chisqtestGC(ScarolinaF_table)
```
The P-value is 2% which is obviously less than 5%. Due to this we will reject the null hypothesis and assume that the aids drug is specific to females.


###MALES

$H_0$ The aids drug is not specific to males. (Independent)

$H_a$ The aids drug is specific to males.

```{r}
ScarolinaM <- filter(Scarolina,sex=="M")
ScarolinaM_table <- xtabs(~infected + group, data = ScarolinaM)
chisqtestGC(ScarolinaM_table)
```
The P-value is 9%, greater than 5%, so we will accept the null hypothesis and assume that the drug is not specific to males.




# Central Africa



##As a Whole

$H_0$ The aids drug is not effective. (Inependent)

$H_a$ The aids drug is effective.

```{r}
cenAfrica_table <- xtabs(~infected + group, data = cenAfrica)
chisqtestGC(cenAfrica_table)
```
The P-value is 57%, accepting the null hypothesis that the drug in Central Africa is not effective.

We will subset the data by sex to see if the drug is sex specific.

###FEMALES

$H_0$ The aids drug is not specific to females. (Independent)

$H_a$ The aids drug is specific to females.

```{r}
cenAfricaF <- filter(cenAfrica, sex=="F")
cenAfricaF_table <- xtabs(~infected + group, data = cenAfricaF)
chisqtestGC(cenAfricaF_table)
```
The P-value is 50%, we accept the null hypothesis and assume that the drug is not specific to females.

###MALES###
$H_0$ The aids drug is not specific to males. (Independent)

$H_a$ The aids drug is specific to males.

```{r}
cenAfricaM <- filter(cenAfrica,sex=="M")
cenAfricaM_table <- xtabs(~infected + group, data = cenAfricaM)
chisqtestGC(cenAfricaM_table)
```
The P-value is 1, we accept the null hypothesis and assume that the drug is independent and not specific to males. 


# Korea

###As a Whole

$H_0$ The aids drug is not effective. (Inependent)

$H_a$ The aids drug is effective.

```{r}
korea_table <- xtabs(~infected + group, data= korea)
chisqtestGC(korea_table)
```

The P-value is 69%, we will accept the null hypothesis and assume that the drug is independent and not effective. 

We will subset the data by sex to see if the drug is sex specific.

###FEMALES

$H_0$ The aids drug is not specific to females. (Inependent)

$H_a$ The aids drug is specific to females.

```{r}
koreaF <- filter(korea,sex=="F")
koreaF_table <- xtabs(~infected + group, data = koreaF)
chisqtestGC(koreaF_table)
```
The P-value is 0 assuming that the drug is specific to females.

###MALES

$H_0$ The aids drug is not specific to males. (Inependent)

$H_a$ The aids drug is specific to males.

```{r}
koreaM <- filter(korea, sex=="M")
koreaM_table <- xtabs(~infected + group, data = koreaM)
chisqtestGC(koreaM_table)
```

The P-value is zero, we reject the null hypothesis and assume that the drug is specific to males. 

